### 2017-04-11 CS798-ConvexityAndOptimization/assignments/project.tex
packing-covering section

The multiplicative weights update method studied in Lecture $9$ is a powerful and ubiquitous tool in algorithm design \cite{arora2012multiplicative}. This method is the workhorse behind the primal-dual paradigm in designing competitive online algorithms \cite{buchbinder2009design}. One major area of application for such algorithms is the design of auctions for selling ad space in search query results.

@@

\item for all $i \in [n]$, $\sum_{j : i \in S(j)} y_j \leq c_i + O(\log d)$.

@@

>>>>

The multiplicative weights update method studied in Lecture $9$ is a powerful and ubiquitous tool in algorithm design \cite{arora2012multiplicative}. This method is the inspiration behind the critical step in the primal-dual paradigm for designing competitive online algorithms \cite{buchbinder2009design}. One major area of application for such algorithms is the design of auctions for selling ad space in search query results.

@@

\item for all $i \in [n]$, $\sum_{j : i \in S(j)} y_j \leq c_i \cdot O(\log d)$.

@@

\paragraph{Connection to Multiplicative Weights}
If we looks at Step $2a$ of $\cA$, we observe multiplicative update rule very similar to those used in the study of the Multiplicative Weights Update Method of Lecture $9$:
$$x_i \leftarrow x_i(1+\frac{1}{c_i}) + 1(|S(j)|\cdot c_i).$$
So each $x_i$ involved in constraint $j$ is increased multiplicatively, while $y_j$ increases additively during the operation of the While loop in Step $2$. Notice that during the proof for the competitive factor we used an induction obtaining that $x_i$ is approximately an exponential function of the $y_j$'s:
$$x_i = \frac{1}{d}((1+\frac{1}{c_i})^{\sum_{j : i \in S(j)} y_j} -1),$$
similar to how we observe an exponential relationship between the potential function (in the proof for the performance guarantee in multiplicative weights update) and the variables of the multiplicative weights update procedure. In both scenarios these exponentials that arise from the respective multiplicative update rules allow us to derive logarithmic performance factors. The difference being that factor is additive in multiplicative update method, and is multiplicative in primal-dual.
